Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-29 paper.tex
fixed the proof of lemma 6
fixed an error related to 1/2 sub-gaussian

\begin{lemma}
Define $\tau$ to be any stopping time that is almost surely between $t_n$ and $t_{n+1}-1$ with respect to the filtration $\mathcal{F}_{t}=\sigma(A_1,\cdots,A_t,c_1,\cdots,c_t,O_1,\cdots,O_t)$, we have 
\begin{align}
P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right), \nonumber
\end{align}
for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
\label{round:prob}
\end{lemma}

@@

\begin{lemma}
For $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$, we have
\begin{align}
\frac{n\lambda}{2\sqrt{2}\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
\end{align}
\label{n0-inequality}
\end{lemma}

\begin{proof}
First, we observe that
\begin{align}
&\frac{n\lambda}{2\sqrt{2}\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)} \nonumber \\
\iff &\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{4.8\sigma^2}{\lambda^2}. \nonumber 
\end{align}
Since $\log(x)\leq x-1$ for $x>0$, we know 
\begin{align}
\log(\log_{1.1}(n)+1)=\log\left(\frac{\log(n)}{\log(1.1)}+1\right)\leq \log(11\log(n)+1)\leq \log(11n)\leq 3+\log(n). \nonumber
\end{align}

@@

To prove the lemma, we just need to show for $n\geq n_{0}$, we have
\begin{align}
\frac{n}{3+\log(n)}\geq \frac{4.8\sigma^2}{\lambda^2}. \label{n0-equ}
\end{align}
Inequality~(\ref{n0-equ}) is true because of the following two observations:
\begin{itemize}
\item for $n\geq 50$, we have $\frac{n}{3+\log(n)}\geq n^{0.5}$;
\item for $n\geq \frac{23.04\sigma^4}{\lambda^4}$, we have $n^{0.5}\geq {4.8\sigma^{2}}{\lambda^{2}}$.
\end{itemize}

@@

To bound equation~(\ref{ACI}), we use Lemma~\ref{ACI-inequality}. Similar to Lemma~\ref{ACI-inequality}, we define
\begin{align}
S_{N(i,\tau)}^{i,j}=\frac{\epsilon_{i,\tau}^{j}}{\sqrt{2}\sigma}. \nonumber
\end{align}

Based on Lemma~\ref{n0-inequality}, for $n_{0}=\max\{50, \frac{23.04\sigma^2}{\lambda^2}\}$ and $n\geq n_{0}$, we have
\begin{align}
\frac{n\lambda}{2\sqrt{2}\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
\end{align}

Thus, if we set $b=\frac{n\lambda^2}{8\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,\tau)\geq n\geq n_{0}$, we have
\begin{align}
\frac{N(i,\tau)\lambda}{\sqrt{2}\sigma}\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)}+\frac{\lambda}{2\sqrt{2}\sigma}\sqrt{n N(i,\tau)} \nonumber \\
\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)+bN(i,\tau)}, \nonumber 
\end{align}
where the last inequality is because $\sqrt{x}+\sqrt{y}\geq \sqrt{x+y}$. Thus, we have
\begin{align}
&P(\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
=&P\left(S_{N(i,\tau)}^{i,j}>\frac{N(i,\tau)\lambda}{\sqrt{2}\sigma}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & P\left(S_{N(i,\tau)}^{i,j}> \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber
\end{align}
Similarily, we can bound 
\begin{align}
&P(\epsilon_{i,\tau}^{j}<-N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
=&P(-\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & 12\exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber 
\end{align}

Therefore, we know $P(\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right)$. Thus, we know
\begin{align}
&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)  \nonumber \\
\leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber
\end{align}

@@

@@

Thus,

\begin{align}
&\sum_{t=1}^{\infty}c(t) \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\} \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
\end{align}

Set $g(n,l)$ to be $\frac{l}{n}$. Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2Wm\lambda\}$, they will correctly identify their best arm. Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{l}{n} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$. Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms. Denote $a_0=\frac{2Wm}{p^{-1}(\frac{p}{2})}$. In order to have $\frac{l}{n}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil a_{0} l\rceil$. In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$. Denote $n_2=\frac{2}{p}$. Thus, we know we can only incur regret for sample paths $\omega$ in the $l^{th}$ envelope in the first $\max\{n_2,\lceil a_0 l\rceil\}$ rounds.

Thus,
\begin{align}
\sum_{t=1}^{\infty}c(t)=\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
\end{align}

@@

\begin{align}
&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}E[c(t)|\omega \in L[l],t\in [t_n,t_{n+1}))P(\omega\in L[l],t\in [t_n,t_{n+1})) \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}\left[R+2Wm\frac{l}{n}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})). \nonumber
\end{align}

We now bound $P(\omega\in L[l]|t\in[t_{n},t_{n+1}))$.
\begin{align}
&P(\omega\in L[l]|t\in[t_{n},t_{n+1})) \nonumber \\
=&P(\omega\in L^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in L^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
\leq & 1-P(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}, \forall i,j|t\in[t_n,t_{n+1})) \nonumber \\
=&P(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{l-1}{n}|t\in[t_n,t_{n+1})) \nonumber  \\
=&\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{l-1}{n}|t\in[t_n,t_{n+1})) \nonumber \\
=&\sum_{i,j}P(|S_{i,t}^{j}|\geq \frac{N(i,t)(l-1)}{n}|t\in[t_n,t_{n+1})) \nonumber 
\end{align}

@@

\begin{lemma}
Under our algorithm, the expected number of payments is bounded above by $O(N^2)$.
\end{lemma}

\begin{proof}
If $|u_{i}^{j}-u_{i,t}^{j}|< \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2mW\lambda\}$, they will correctly identify their best arm. Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|< \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms. In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$. Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$. Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).The cumulative expected number of payments is bounded above by:

Define $\tau_{n}^{k}$ to be a stopping time which equals to the $k_{th}$ time period in the $n^{th}$ round. Then
\begin{align}
&\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\} \nonumber \\
=&\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}\sum_{t=k}^{\infty}\mathbbm{1}\{c(t)>0\}\mathbbm{1}\{t=\tau_{n}^{k}\} \nonumber 
\end{align}

Thus, we know
\begin{align}
&E[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}] \nonumber \\
\leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}\sum_{k=1}^{\infty}P\left(\exists i,j:|u_{i}^{j}-u_{i,\tau_{n}^{k}}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2Wm}\right)P(t=\tau_{n}^{k})+\sum_{n=1}^{n_1}N \nonumber \\
\leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}\sum_{k=1}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{32m^2\sigma^2}\right)\times P(t=\tau_{n}^{k})+\sum_{n=1}^{n_1}N \nonumber \\
\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{32m^2\sigma^2}\right)\times Nn+\sum_{n=1}^{n_1}N \nonumber  \\
=&24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2} + Nn_1, \nonumber
\end{align}

@@

For regret incurred after the first $n_0$ round, it has two different components: the regret incurred when we let the agents play myopically and the regret incurred when we incentivize the agents. For the regret incurred when we let the agents play myopically at time t, it consists of the following two components:
\begin{itemize}
\item For those user whose utility difference between their best and the second best arm is greater than $f(t)$: suppose it is at the $n(t)^{th}$ round, the probability of these user making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n(t) f(t)^2}{32 m^2\sigma^2}\right)$ at time $t$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n(t) f(t)^2}{32 m^2\sigma^2}\right)\times R$. We denote the regret incurred by these agents as $r_1(t)$.
\item For those user whose utility difference between their best and the second best arm is smaller than $f(t)$: this happens with probability $S(f(t))$ at each time and regret is bounded above by $S(f(t)) \times f(t)=Mf(t)^2$. We denote the regret incurred by these agents as $r_2(t)$.
\end{itemize}

>>>>

\begin{lemma}
Define $\tau$ to be any stopping time that is almost surely between $t_n$ and $t_{n+1}-1$ with respect to the filtration $\mathcal{F}_{t}=\sigma(A_1,\cdots,A_t,c_1,\cdots,c_t,O_1,\cdots,O_t)$, we have 
\begin{align}
P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{16\sigma^2}\right), \nonumber
\end{align}
for $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$.
\label{round:prob}
\end{lemma}

@@

\begin{lemma}
For $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$, we have
\begin{align}
\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
\end{align}
\label{n0-inequality}
\end{lemma}

\begin{proof}
First, we observe that
\begin{align}
&\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)} \nonumber \\
\iff &\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{9.6\sigma^2}{\lambda^2}. \nonumber 
\end{align}
Since $\log(x)\leq x-1$ for $x>0$, we know 
\begin{align}
\log(\log_{1.1}(n)+1)=\log\left(\frac{\log(n)}{\log(1.1)}+1\right)\leq \log(11\log(n)+1)\leq \log(11n)\leq 3+\log(n). \nonumber
\end{align}

@@

To prove the lemma, we just need to show for $n\geq n_{0}$, we have
\begin{align}
\frac{n}{3+\log(n)}\geq \frac{9.6\sigma^2}{\lambda^2}. \label{n0-equ}
\end{align}
Inequality~(\ref{n0-equ}) is true because of the following two observations:
\begin{itemize}
\item for $n\geq 50$, we have $\frac{n}{3+\log(n)}\geq n^{0.5}$;
\item for $n\geq \frac{92.16\sigma^4}{\lambda^4}$, we have $n^{0.5}\geq {9.6\sigma^{2}}{\lambda^{2}}$.
\end{itemize}

@@

To bound equation~(\ref{ACI}), we use Lemma~\ref{ACI-inequality}. Similar to Lemma~\ref{ACI-inequality}, we define
\begin{align}
S_{N(i,\tau)}^{i,j}=\frac{\epsilon_{i,\tau}^{j}}{2\sigma}. \nonumber
\end{align}

Based on Lemma~\ref{n0-inequality}, for $n_{0}=\max\{50, \frac{92.16\sigma^2}{\lambda^2}\}$ and $n\geq n_{0}$, we have
\begin{align}
\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
\end{align}

Thus, if we set $b=\frac{n\lambda^2}{16\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,\tau)\geq n\geq n_{0}$, we have
\begin{align}
\frac{N(i,\tau)\lambda}{2\sigma}\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)}+\frac{\lambda}{4\sigma}\sqrt{n N(i,\tau)} \nonumber \\
\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)+bN(i,\tau)}, \nonumber 
\end{align}
where the last inequality is because $\sqrt{x}+\sqrt{y}\geq \sqrt{x+y}$. Thus, we have
\begin{align}
&P(\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
=&P\left(S_{N(i,\tau)}^{i,j}>\frac{N(i,\tau)\lambda}{2\sigma}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & P\left(S_{N(i,\tau)}^{i,j}> \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
\end{align}
Similarily, we can bound 
\begin{align}
&P(\epsilon_{i,\tau}^{j}<-N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
=&P(-\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber 
\end{align}

Therefore, we know $P(\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right)$. Thus, we know
\begin{align}
&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)  \nonumber \\
\leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
\end{align}

@@

We also need the following lemma in part of the proof of Theorem~\ref{rst:budget}.
\begin{lemma}
For all $n\geq 1$ and $l\geq 2$, we have
\begin{align}
0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}. \nonumber
\end{align}
\label{lemma:cal2}
\end{lemma}
\begin{proof}
\begin{align}
&0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)} \nonumber \\
\iff & 0.81 n^{5/3} \geq 0.6n \log(\log_{1.1}(n)+1) \nonumber \\
\Longleftarrow &  1.3 n^{2/3} \geq  \log(\log_{1.1}(n)+1) \nonumber
\end{align}
\end{proof}

@@

We know
\begin{align}
&\sum_{t=1}^{\infty}c(t) \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\} \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
\end{align}

Set $g(n,l)$ to be $\frac{2\sigma l}{n^{1/6}}$. Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2Wm\lambda\}$, they will correctly identify their best arm. Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{2\sigma l}{n^{1/6}} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$. Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms. Denote $a_0=\frac{4Wm\sigma}{p^{-1}(\frac{p}{2})}$. In order to have $\frac{2\sigma l}{n^{1/6}}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil (a_{0} l)^6 \rceil$. In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$. Denote $n_2=\frac{2}{p}$. Thus, we know we can only incur regret for sample paths $\omega$ in the $l^{th}$ envelope in the first $\max\{n_2,\lceil (a_0 l)^6 \rceil\}$ rounds.

Thus,
\begin{align}
\sum_{t=1}^{\infty}c(t)=\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
\end{align}

@@

\begin{align}
&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}E[c(t)|\omega \in L[l],t\in [t_n,t_{n+1}))P(\omega\in L[l],t\in [t_n,t_{n+1})) \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+2Wm\frac{2\sigma l}{n^{1/6}}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})). \nonumber
\end{align}

We now bound $P(\omega\in L[l]|t\in[t_{n},t_{n+1}))$ for $n\geq n_0$ and $l\geq 2$.
\begin{align}
&P(\omega\in L[l]|t\in[t_{n},t_{n+1})) \nonumber \\
=&P(\omega\in L^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in L^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
\leq & 1-P(|\epsilon_{i,t}^{j}|<\frac{2\sigma (l-1)}{n^{1/6}}, \forall i,j|t\in[t_n,t_{n+1})) \nonumber \\
=&P(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber  \\
=&\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber
\end{align}

Define $S_{i,t}^{j}=\frac{N(i,t)\epsilon_{i,t}^{j}}{2\sigma}$, then we know $S_{i,t}^{j}$ is a summation of $1/2$ gaussian random numbers. Therefore,

\begin{align}
&\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{l-1}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber \\ 
=&\sum_{i,j}P(|S_{i,t}^{j}|\geq \frac{N(i,t)(l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})). \nonumber \\
\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})). \nonumber
\end{align}

Based on Lemma~\ref{lemma:cal2}, we know
\begin{align}
&N(i,t)^{5/6}(l-1) \nonumber \\
=& 0.9N(i,t)^{5/6} + N(i,t)^{5/6}(l-1.9) \nonumber \\
\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)} + \sqrt{(l-1.9)^2 N(i,t)} \nonumber \\
\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+(l-1.9)^2 N(i,t)}. \nonumber
\end{align}

Based on Lemma~\ref{ACI-inequality}, we know
\begin{align}
&\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})) \nonumber \\
\leq & \sum_{i,j}24e^{-1.8(l-1.9)^2} = 24Nme^{-1.8(l-1.9)^2}. \nonumber
\end{align}

Thus,
\begin{align}
&\sum_{t=1}^{\infty}c(t) \nonumber \\
\leq&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+2Wm\frac{2\sigma l}{n^{1/6}}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
\leq& \sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(\omega\in L[1]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
+&\sum_{l=2}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
\leq& \sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(t\in [t_n,t_{n+1})) \nonumber \\
+&\sum_{l=2}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]24Nme^{-1.8(l-1.9)^2}P(t\in [t_n,t_{n+1})) \nonumber \\
\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]Nn +\sum_{l=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]24Nme^{-1.8(l-1.9)^2}Nn \nonumber \\
\leq & \left[R+4Wm\sigma \right]N (\max\{n_2,\lceil (a_0)^6 \rceil\})^2+\sum_{l=2}^{\infty}24N^2 m[R+4Wml\sigma](\max\{n_2,\lceil (a_0 l)^6 \rceil\})^2 e^{-1.8(l-1.9)^2} \nonumber \\
=& O(N^2). \nonumber
\end{align}

@@

\begin{lemma}
Under our algorithm, the expected number of payments is bounded above by $O(N^2)$.
\label{lemma:numP}
\end{lemma}

\begin{proof}
If $|u_{i}^{j}-u_{i,t}^{j}|< \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2mW\lambda\}$, they will correctly identify their best arm. Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|< \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms. In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$. Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$. Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).The cumulative expected number of payments is bounded above by:

Define $\tau_{n}^{i}$ to be the first time we pull arm $i$ in the $n^{th}$ round. Then
\begin{align}
\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\} =\sum_{n=1}^{\infty}\sum_{i=1}^{N}\mathbbm{1}\{c(\tau_{n}^{i})>0\}. \nonumber
\end{align}

Thus, we know
\begin{align}
&E[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}] \nonumber \\
=&\sum_{n=1}^{\infty}\sum_{i=1}^{N}P(c(\tau_{n}^{i})>0) \nonumber \\
\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}P\left(\exists i,j:|u_{i}^{j}-u_{i,\tau_{n}^{i}}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2Wm}\right)+\sum_{n=1}^{n_1}N \nonumber \\
\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right) +\sum_{n=1}^{n_1}N \nonumber \\
\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right)\times N+\sum_{n=1}^{n_1}N \nonumber  \\
\leq&24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1, \nonumber
\end{align}

@@

For regret incurred after the first $n_0$ round, it has two different components: the regret incurred when we let the agents play myopically and the regret incurred when we incentivize the agents. Using Lemma~\ref{lemma:numP}, the expected regret incurred when we incentivize the agents is bounded above by: $\left[24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{32W^2 m^2\sigma^2})-1} + Nn_1\right]R$.

For the regret incurred when we let the agents play myopically at time $t\geq t_{n_0}$, it consists of the following two components:
\begin{itemize}
\item For those users whose utility difference between their best and the second best arm is greater than $f(t)$: we define a sequence of stopping time $\tau_{n}^{k}=t_n+k$.  For the regret occurred at each stopping time $\tau(k)$,  the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau(k))^2}{32 W^2 m^2\sigma^2}\right)$ at stopping time $\tau(k)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau(k))^2}{32 W^2 m^2\sigma^2}\right)\times R$. We denote the regret incurred by these agents as $r_1(\tau(k))$.
\item For those user whose utility difference between their best and the second best arm is smaller than $f(t)$: this happens with probability $S(f(t))$ at each time and regret is bounded above by $S(f(t)) \times f(t)=Mf(t)^2$. We denote the regret incurred by these agents as $r_2(t)$.
\end{itemize}
